How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-25 tse-paper/content.tex
lit survey improvements

% TODO: What about the alternate solution, installing plugins to report
% precise data? Ie., maven plugins
% - Lots of effort
% - not a generic solution
% - how to analyze history where such plugins were not installed
% - unclear which information you want

@@

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature study (step 1).
The literature
survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
natural language processing, information retrieval, or searching
for keywords.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
% TODO fill-in X
only X independent implementations are available, one of which stems
from the second author of this paper.
Out of these implementations, all are based on either a custom parser
or regular expressions.
%Using 1) a set of
% manually curated regular expressions,
% similar to TravisTorrent~\cite{beller2017oops},
% 2) information
% retrieval techniques,
% % todo: Can you shortly explain the technique here?
% and 3) a list of search keywords
% to identify regions of interest in the build log.

@@

In this section, we survey the emerging field of build log
analysis.
We start with a differentiation to the related field of general
system log analysis.
Then, we describe the methodology and results of a systematic mapping
study to
determine the state-of-research on build log analysis following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}.

We close by summarizing how build logs are commonly
analyzed in literature and discuss the implications of these findings.

@@

First, we filtered articles based on (a) their title and (b) the
contextual information Google Scholar displayed.
We included works at large that seemed to bear a resemblance to software
engineering and building software.
We excluded works written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here
With these 256 remaining articles, we followed a backward snowball
sampling for related work.
If an article referenced a new work in the context
of build log analysis, we added the new one to the literature set.
This added five articles (eight before
duplicate elimination), leading to a total of 261
works.

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
% TODO (resolved): All of these are passive
% TODO (resolved) Swap RQ 1.2 and RQ 1.1 (logical order?)
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is extracted from build logs?
  \item[\textbf{RQ1.2:}] Which extraction techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}

@@

To guide the data extraction we created a template.
The template form contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a
pilot study:
both authors extracted data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 46 articles evenly between the two authors
and inspected them as closely as necessary to fill out the template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.
For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.
An example for this is the source of the analyzed build logs,
where we assigned tags such as ``Travis CI'',
``Industrial'', ``Google'', or
``self built''.
Once we had classified all works, we went into the second phase
(``execution phase'') in which we grouped tags
together and found synonyms.
% the following adds to the example but is maybe unneeded / too much
For instance, in the case of the build log source we grouped
``Travis'' and ``travis ci'' together and assigned ``Industrial'' to
all articles that used build logs provided by a company.

The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.

@@

\raisebox{0.8mm}{Information Retrieval} &
\raisebox{0.8mm}{
\cite{hassan2017change,lindqvist2019detection,ren2018automated}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
% TODO: We need to mention in the text describing the Table what we mean
by ``Analysis''
\raisebox{0.8mm}{Analysis} &
\raisebox{0.8mm}{
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

@@

\subsubsection{Which information is targeted? (RQ 1.1)}
% TODO General ref to Figure 4 missing: We answer this question along
% data in Figure 4, and ...
% ?

@@

% TODO It is unclear where this comes from.
% TODO Also, wouldn't it perhaps be better to continue with Figure
%4.b directly?
In most cases (51\%), a chunk was retrieved from the log.
Build logs were scanned for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, distinguishing failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

The majority of articles (46\%) used the outcome of their build log
analysis for research purposes, as shown in \Cref{fig:litsur:use}.
% TODO What does this mean? Give an example: to drive further research,
%FIXME
for example to categorize the types of compile errors encountered at
Google~\cite{seo2014programmers}.
Further uses were giving feedback to developers (10\%) or automatic
on-ward processing of the retrieved information (8\%)
% TODO for example to ...
%FIXME
.

\subsubsection{Which techniques are used? (RQ 1.2)}
\Cref{tab:litsur:techniques} presents the techniques that the articles
described for analyzing build logs.
43 of the 61 articles we inspected mentioned how they are analyzing
build logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs''
~\cite{rahman2018impact}.
% TODO maybe make the point here that it is questionable whether this
%includes a comprehensive tokenizer, lexer etc.
%based solution and that parsing in many cases really meant regexp.
%If we could figure that out, then we would assign it to regexp instead.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating}
% (based on regular expressions),
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
% based on which technique?,  (based on regular expressions)
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
% based on which technique?  (a parser for the output of make files)
.
% I don't think the based on..
%adds something here.
% It's all kinda regex.
%Even if we say 'parser' it's often regex in the background

\subsubsection{Which build logs are analyzed? (RQ 1.3)}
\Cref{fig:litsur:log_producer} shows the distribution of supported
build tools.
Of the articles we surveyed, 30\% analyzed
Maven~\cite{maven2019website} build logs,
16\% analyzed Gradle~\cite{gradle2020website} logs
and 10\% analyzed Ant~\cite{ant2020website} logs.

% TODO remove first part of this paragraph?
Sometimes, aspects separate from the build log analysis motivate
this limitation to a specific build tool.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.
A larger amount of the articles within the survey, however, limit
themselves to few build tools because their log format varies and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.

@@

% TODO perhaps remove this paragraph?
% yes it is very unspecific.
%however then we have 0 reference
% to how many logs are analyzed
% a central point in our argumentation for automation
The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported analyzing from two up to 122 million logs.

31\% of the surveyed articles claimed to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying}, and several other studies reused.

@@

Several articles noted the variety in log formats for different build
environments, which requires customizing build log techniques for
every supported build environment.
\Cref{fig:litsur:log_producer} shows that many studies and tools target
only a few distinct build environments (roughly, area A).
% TODO: passive ...
The majority of build environments was however only targeted by one
article each (B).
From this, we follow: (a) there is a niche for custom parsers or even
specialized plugins integrated into the build process to make
post-factum
parsing of logs redundant.
Plugins  similar to, for example, the Maven plugin to report test
executions Bell et al.
%TODO cite
wrote, still have the disadvantage of not being able to work on historic
builds.
(b) the large tail of seldomly-investigated environments would benefit
from the existence of a more generic
solution.
% We implement build environment agnostic build log analysis
% techniques, which are customized to a specific project by
% the training examples which the user provides.
% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
% data set we chose for our evaluation covers a broad range of build
% environments.
% % Further, the training examples also specify the log chunk targeted
% by the
% % retrieval, which enable our chunk retrieval techniques to retrieve
% % a broad range of information from build logs.

% TODO this is disconnected, at least here
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone,'' other
articles pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.

@@

@@

% Moritz: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% TODO Caro: Can you given an example of such an error message?
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
% Why does it return an error message? Shouldn't it also return
% <empty string>? Does it not rather return an error message if no
% program can be synthesized?
% TODO Moritz: a regular expression can match an empty string
% and that is different from not finding a match
% it returns error messages in both cases
% TODO: Ok, but what is the point of matching on an empty string?
(if I understand what you mean)? you would not normally define such
an extraction?
% If this distinction is important it needs to be made more clear
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

@@

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
% Moritz: I think it is good, but the VSM is still unexplained.
%We need a
% (at least) 1-sentence introduction to it, at its first reference
% TODO Moritz: I removed all other references, this is now the first one.
% I hope I got your comment right and now the first and only reference
% is explained :)
% TODO Slightly better, but I still have a problem with this -- what
% exactly is the vector
% space model here?
% At a minimum, the text should mention what the vector is and how the
model is used
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in this case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

\subsection{Study Process}
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
We vary its size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of the techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
%of results?
% motivation why only one test example.
% we can also leave that out
% and answer if we are asked about it
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% TODO what about referencing the combined figure at first: something
%like shows the results of CTS on two beanplots of ...
%and ...., and then the subfigure
% TODO this goes for all techniques
% TODO QUESTION: yes, though then we have more redundant text
% that repeats everywhere and is already in the captions
% -> should we add it for the first time we include a type of figure?
% TODO Yes, that sounds good.
You might even say Figure 12-15 show two
% plots in the short text under the section heading.
It just makes the
% text flow so much better.
\Cref{fig:recall-precision-examplecount-CTS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using CTS for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.

>>>>

%\section{introduction}
% TODO: What about the alternate solution, installing plugins to report
% precise data? Ie., maven plugins
% - Lots of effort
% - not a generic solution
% - how to analyze history where such plugins were not installed
% - unclear which information you want

@@

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature study (step 1).
The literature
survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
natural language processing, information retrieval, or searching
for keywords.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
% TODO Moritz: 14 is still quite big, it's 'impl available' when we saw
% no overlap.
Decide whether you want to keep this in :)
only 14 independent implementations are available, one of which stems
from the second author of this paper.
Out of these implementations, all are based on either a custom parser
or regular expressions.
%Using 1) a set of
% manually curated regular expressions,
% similar to TravisTorrent~\cite{beller2017oops},
% 2) information
% retrieval techniques,
% % Can you shortly explain the technique here?
% and 3) a list of search keywords
% to identify regions of interest in the build log.

@@

In this section, we survey the emerging field of build log
analysis.
We start with a differentiation to the related field of
system log analysis.
% ref to fig 2 so it can be here and above fig 3
Then, we describe the methodology (\Cref{fig:lit-survey})
and results of a systematic mapping
study to
determine the state-of-research on build log analysis following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}.
We close by summarizing how build logs are commonly
analyzed in literature and discuss the implications of these findings.

@@

First, we filtered articles based on (a) their title and (b) the
contextual information Google Scholar displayed.
We included works at large that seemed to bear a resemblance to software
engineering and building software.
We excluded works written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here

With these 256 remaining articles, we followed a backward snowball
sampling for related work.
If an article referenced a new work in the context
of build log analysis, we added the new one to the literature set.
This added five articles (eight before
duplicate elimination), leading to a total of 261
works.

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
% TODO (resolved): All of these are passive
% it says resolved, but they still are?
% I exchanged 'extracted' with targeted / analysis
% 'information retrieved' or 'information extracted' will give us
% this is not IR neither IE discussions again
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}

@@

To guide the data extraction we created a template.
The template form contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a
pilot study:
both authors extracted data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 56 articles evenly between the two authors
and inspected each as closely as necessary to fill out the template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.

For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.
An example for this is the source of the analyzed build logs,
where we assigned tags such as ``Travis CI'',
``Industrial'', ``Google'', or
``self built''.
Once we had classified all works, we went into the second phase
(``execution phase'') in which we grouped tags
together and found synonyms.
% the following adds to the example but is maybe unneeded / too much
For instance, in the case of the build log source we grouped
``Travis'' and ``travis ci'' together and assigned ``Industrial'' to
all articles that used build logs provided by a company.
The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.

@@

\raisebox{0.8mm}{Information Retrieval} &
\raisebox{0.8mm}{
\cite{hassan2017change,lindqvist2019detection,ren2018automated}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
% TODO: We need to mention in the text describing the Table what we mean
%by ``Analysis''
\raisebox{0.8mm}{Analysis} &
\raisebox{0.8mm}{
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

@@

\subsubsection{What information is targeted in build logs? (RQ 1.1)}

@@

\Cref{fig:litsur:use} shows the reason for the
investigated articles to analyze build logs.
The majority of articles (46\%) used the outcome of their build log
analysis to drive further research.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other articles (10\%) used the gained insights to give feedback to
developers.
For 8\% of the articles the retrieved information was the input
to a next automatic on-ward processing step.
Articles chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

We also identified the type of information which the articles
retrieved from the build logs.
In most cases (51\%), the researchers retrieved a chunk of text.
They scanned build logs for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, they distinguish failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
determine whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

\subsubsection{Which analysis techniques exist? (RQ 1.2)}
\Cref{tab:litsur:techniques} presents the techniques that the articles
described for analyzing build logs.
43 of the 61 articles we inspected mentioned how they are analyzing
build logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs''
~\cite{rahman2018impact}.
For such imprecise statements it was often not clear if they describe
a complex parser (including a tokenizer, lexer, etc.) or refer to a
simpler parsing tool based on regular expressions.
If we saw evidence for the latter, we assigned the tag
``regular expression'' instead of the tag ``parser''.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool.

\subsubsection{Which kinds of build logs are subject to
  analysis? (RQ 1.3)}
\Cref{fig:litsur:log_producer} shows the distribution of supported
build tools.
Of the articles we surveyed, 30\% analyzed
Maven~\cite{maven2019website} build logs,
16\% analyzed Gradle~\cite{gradle2020website} logs
and 10\% analyzed Ant~\cite{ant2020website} logs.

A large amount of the articles within the survey, analyze build logs
from a small number of build tools.
In most cases, this is because the format of build logs changes
~\cite{staahl2014modeling} and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.
% remove following part of this paragraph?
% I think it is a nice anecdote but not super necessary yes.
Sometimes, aspects separate from the build log analysis motivate
their limitation to a specific build tool.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.

@@

% perhaps remove this paragraph?
% C: made it more specific, this is the only reference in the result
% which supports 'we need automatic because so many logs are analy'
The number of logs analyzed varied greatly between the articles
and we were not always able to
extract it confidently.
23 of the articles analyzed more than a thousand build logs, some
investigated up to 122 million logs.

31\% of the surveyed articles claimed to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying},
and several other articles studied.

@@

Several articles noted the variety in log formats for different build
environments, which requires customizing build log techniques for
every supported build environment.
\Cref{fig:litsur:log_producer} shows that many studies and tools target
only a few distinct build environments (roughly, area A).
% TODO: passive ...
The majority of build environments was however only targeted by one
article each (B).
From this, we follow: (a) there is a niche for custom parsers or even
specialized plugins integrated into the build process to make
post-factum
parsing of logs redundant.
Plugins  similar to, for example, the Maven plugin to report test
executions Bell et al.
%TODO cite
wrote, still have the disadvantage of not being able to work on historic
builds.
(b) the large tail of seldomly-investigated environments would benefit
from the existence of a more generic
solution.
% TODO this is disconnected, at least here
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone,'' other
articles pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.

% We implement build environment agnostic build log analysis
% techniques, which are customized to a specific project by
% the training examples which the user provides.
% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
% data set we chose for our evaluation covers a broad range of build
% environments.
% % Further, the training examples also specify the log chunk targeted
% by the
% % retrieval, which enable our chunk retrieval techniques to retrieve
% % a broad range of information from build logs.

@@

\subsection{The case for chunk retrieval on build logs}

@@

% Moritz: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% TODO Caro: Can you given an example of such an error message?
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
% Why does it return an error message? Shouldn't it also return
% <empty string>? Does it not rather return an error message if no
% program can be synthesized?
% TODO Moritz: a regular expression can match an empty string
% and that is different from not finding a match
% it returns error messages in both cases
% TODO: Ok, but what is the point of matching on an empty string?
%(if I understand what you mean)? you would not normally define such
%an extraction?
% If this distinction is important it needs to be made more clear

% TODO CARO: make more clear that not matching is an error cause
% pattern didn't match?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

@@

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
% Moritz: I think it is good, but the VSM is still unexplained.
%We need a
% (at least) 1-sentence introduction to it, at its first reference
% TODO Moritz: I removed all other references, this is now the first one.
% I hope I got your comment right and now the first and only reference
% is explained :)
% TODO Slightly better, but I still have a problem with this -- what
% exactly is the vector
% space model here?
% At a minimum, the text should mention what the vector is and how the
% model is used
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in this case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

\subsection{Study Process}
% FIXME introduce term example
% FIXME mention study figure
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
We vary its size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of the techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
%of results?
% motivation why only one test example.
% we can also leave that out
% and answer if we are asked about it
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% TODO what about referencing the combined figure at first: something
%like shows the results of CTS on two beanplots of ...
%and ...., and then the subfigure
% TODO this goes for all techniques
% TODO QUESTION: yes, though then we have more redundant text
% that repeats everywhere and is already in the captions
% -> should we add it for the first time we include a type of figure?
% TODO Yes, that sounds good.
% FIXME CARO You might even say Figure 12-15 show two
% plots in the short text under the section heading.
% It just makes the
% text flow so much better.
\Cref{fig:recall-precision-examplecount-CTS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using CTS for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.
